Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Add template code for GLAD/EDGI gender bar chart

@@

alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
```

@@

RETROSPECTIVE
```{r subset retrospective data }
dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
        (data_group_pcl == "Baseline data only" |
           data_group_pcl == "Baseline and retrospective data" |
            data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

dim(dat.retro)
```

@@

>>>>

```{r Clean environment}

remove(list = ls())

@@

alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)

alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)

@@

RETROSPECTIVE
```{r subset retrospective data }

dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
        (data_group_pcl == "Baseline data only" |
           data_group_pcl == "Baseline and retrospective data" |
            data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

dim(dat.retro)

@@

#Histograms

##Gender
###Prepan

```{r GLAD/EDGI gender prepan histogram}

GLAD.prepan %>%
  ggplot(aes(x = Gender)) +
  geom_bar(fill = "black") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Gender distribution of the GLAD/EDGI Cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants")
